Article Title

### 2019-08-25 text/02-methods.Rmd
Wrote short intro about choosing quality metric

>>>>

## Choosing the right evaluation metric
A plethora of different metric to evaluate the quality of functional annotation predictions is available using different approaches and there seems to be no clear standard yet. `TODO: THIS IS WEAK`
Additionally, each of the metrics has a different focus and lalala so choosing a metric for quality evaluation is not trivial.
When we first published GOMAP [@Wimalanathan2018], we used a modified version of the hierarchical evaluation metrics originally introduced in [@Verspoor2006] because they were simple, clear, and part of an earlier attempt at unifying and standardizing GO annotation comparisons [@Defoin-Platel2011].
In the meantime, @Plyusnin2018 have published an approach for evaluating different metrics showing substantial differences within the robustness of different approaches.
`TODO DESCRIBE THEIR APPROACH`
We have applied their method on the Gold Standards available to us to determine which evaluation metric is the most appropriate in our case.
The results of this analysis can be seen in `TODO`.

We then evaluated our predictions and the other annotation sets using the best performing metrics as well as the one we previously used.
`TODO`

### 2019-08-25 text/index.Rmd
Wrote short intro about choosing quality metric

---
title: "Article Title"
runtitle: "Short Title"
documentclass: frontiersSCNS  # or frontiersHLTH, or frontiersFPHY
author:
  - name: First Author
    affiliation: '1'
    etal: LASTNAME # First author's last name. 
  - name: Co-Author
    affiliation: '2'
  - name: Co-Author
    affiliation: '1,3'
    email: email@uni.edu # Indicates corresponding Author
    institution: Laboratory X, Institute X, Department X, Organization X
    street: Street X
    city: City X
    state: State XX # only USA, Australia, Canada
    zip: Zip Code X
    country: Country X
affiliation:
  - id: '1'
    department: Department X
    institution: Institution X
    city: City X
    state: State XX # only USA, Australia, Canada
    country: Country X
  - id: '2' 
    department: Department X
    institution: Institution X
    city: City X
    state: State XX # only USA, Australia, Canada
    country: Country X
  - id: '3' 
    department: Department X
    institution: Institution X
    city: City X
    state: State XX # only USA, Australia, Canada
    country: Country X
date: "Febcember 32nd 3023"
language: en-US
site: "bookdown::bookdown_site"
csl: frontiers.csl
bibliography: test.bib
link-citations: true
output:
  bookdown::pdf_book:
    keep_tex: true
    keep_md: true
    base_format: rticles::frontiers_article
    citation_package: natbib
    includes:
      in_header:
        preamble.tex
---

>>>>

---
title: "Article Title"
runtitle: "Short Title"
documentclass: frontiersSCNS  # or frontiersHLTH, or frontiersFPHY
author:
  - name: First Author
    affiliation: '1'
    etal: LASTNAME # First author's last name. 
  - name: Co-Author
    affiliation: '2'
  - name: Co-Author
    affiliation: '1,3'
    email: email@uni.edu # Indicates corresponding Author
    institution: Laboratory X, Institute X, Department X, Organization X
    street: Street X
    city: City X
    state: State XX # only USA, Australia, Canada
    zip: Zip Code X
    country: Country X
affiliation:
  - id: '1'
    department: Department X
    institution: Institution X
    city: City X
    state: State XX # only USA, Australia, Canada
    country: Country X
  - id: '2' 
    department: Department X
    institution: Institution X
    city: City X
    state: State XX # only USA, Australia, Canada
    country: Country X
  - id: '3' 
    department: Department X
    institution: Institution X
    city: City X
    state: State XX # only USA, Australia, Canada
    country: Country X
date: "Febcember 32nd 3023"
language: en-US
site: "bookdown::bookdown_site"
csl: frontiers.csl
link-citations: true
output:
  bookdown::pdf_book:
    keep_tex: true
    keep_md: true
    base_format: rticles::frontiers_article
    citation_package: natbib
    includes:
      in_header:
        preamble.tex
---
